\bfseries Don't interpolate your data!

### 2022-10-17 main.tex
notes to self

We show the results of Standar Practice (tm), for the fake data, in \figurename~\ref{fig:standard}.
We also show the comparison with the true spectral expectation model that was employed to make the fake data.
We find HOGG WHAT??

\paragraph{Our method: Forward Model (tm)}
HOGG: OUR METHOD NEEDS A CONSISTENT NAME USED THROUGHOUT. FORWARD MODEL??

@@

@@

How do you modify to deal with LSF variations (like we have in \textsl{SDSS-V APOGEE}?

>>>>

We show the results of Standard Practice (tm), for the fake data, in \figurename~\ref{fig:standard}.
We also show the comparison with the true spectral expectation model that was employed to make the fake data.
We find HOGG WHAT??

\paragraph{Fiducial case}
HOGG: OUR METHOD NEEDS A CONSISTENT NAME USED THROUGHOUT. FORWARD MODEL??

HOGG: Give full list of input parameters for the Fiducial.

@@

\paragraph{Dependence on raw-data pixel scale}
HOGG show that things with Standard Practice (tm) depend VERY STRONGLY on the input pixel grid.

\paragraph{Noise and noise covariances}
HOGG do repeated trials to empirically measure the noise covariances.

Plot the empirical covariances as a function of input-data pixel scale, interpolation method, and number of epochs.

@@

How do you modify to deal with LSF variations (like we have in \textsl{SDSS-V APOGEE}?
What if you don't know the LSF differences?
Difference between modeling LSF changes and modeling LSFs. The former is good, the latter is bad.
